The Way Forward in Parallelizing Dynamic Languages

### 2014-05-01 talk/icooolps2014/position-paper.tex
add some handwavy comparison table

\usepackage[utf8]{inputenc}

\usepackage{amsmath}

@@

\section{The Way Forward}
possible solution:\\
- use virtual memory paging to somehow lower the STM overhead\\
- tight integration with GC and jit?

>>>>

\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{amsmath}

@@

\section{The Way Forward}
\begin{table}[]
  \centering
  \begin{tabular}{|p{2cm}|c|c|c|c|c|}
    \hline
    & \textbf{GIL} & \parbox[t]{1cm}{\textbf{Fine-grained locking}}
    & \parbox[t]{1cm}{\textbf{Shared-nothing}} & \textbf{HTM} & \textbf{STM}\\
    \hline
    Performance            & 0  & +  & ++   & +  & -{-} \\
    \hline
    Existing applications  & ++ & ++ & -{-} & ++ & ++   \\
    \hline
    Better synchronization & 0  & 0  & -    & -  & ++   \\
    \hline
    Implementation         & ++ & -  & ++   & ++ & ++   \\
    \hline
    External libraries     & ++ & ++ & ++   & ++ & ++   \\
    \hline
  \end{tabular}
  \caption{Comparison (--/-/0/+/++)}
  \label{tab:comparison}
\end{table}

Comparison in Table \ref{tab:comparison}

possible solution:\\
- use virtual memory paging to somehow lower the STM overhead\\
- tight integration with GC and jit?
